---
title: "Nor'eastR 2018 Tweets"
author: Jeff Hollister (borrowed from François Michonneau)
output:
   html_document:
     toc: true
---

```{r setup, echo=FALSE, output="hide"}
library(wesanderson)
library(tidyverse)
library(stringr)
library(magick)
library(tidytext)
library(widyr)
library(rvest)

"print.magick-image" <- function(x, ...){
  ext <- ifelse(length(x), tolower(image_info(x[1])$format), "gif")
  tmp <- tempfile(fileext = paste0(".", ext))
  image_write(x, path = tmp)
  knitr::include_graphics(tmp)
}
```


```{r update_tweets, echo=FALSE}

load("noreastr2018.rda")

```

```{r tweet-data, echo=FALSE}
load("noreastr2018.rda")
tw <- noreastr2018 %>%
  distinct(status_id, .keep_all = TRUE)

```

## About this document

This document was generated using RMarkdown, and the source is available on
GitHub at:
[https://github.com/fmichonneau/evol2017-tweets](https://github.com/fmichonneau/evol2017-tweets).

Pull requests to add other figures or fix bugs are welcome.

This document (and associated code) is released under a CC0 licence.

If you have questions or comments, I am on twitter at
[fmic_](https://twitter.com/fmic_) or by email at [francois.michonneau@gmail.com](mailto:francois.michonneau@gmail.com)


## Basic summary

* Total number of tweets with the #Evol2017 hashtag between `r range(tw$created_at)[1]`, and `r range(tw$created_at)[2]`: `r nrow(tw)`
* Total of original tweets (no retweets): `r sum(!tw$is_retweet)`.
* Number of users who tweeted: `r length(unique(tw$screen_name))`.


## The 5 most favorited tweets

```{r top-fav, echo=FALSE, results='asis'}
top_fav <- tw %>%
    filter(!is_retweet) %>%
    top_n(5, favorite_count) %>%
    arrange(desc(favorite_count))

render_tweet <- function(dt, row) {
    screen_name <- dt$screen_name[i]
    id <- format(dt$status_id[i], scientific = FALSE)
    txt <- dt$text[i]
    created <- format(dt$created_at[i], "%Y-%m-%d")
    n_fav <- dt$favorite_count[i]
    n_retweets <- dt$retweet_count[i]
    cat("<blockquote class=\"twitter-tweet\" lang=\"en\"> \n",
        "<p lang=\"en\" dir=\"ltr\">",
        txt,
        "</p>&mdash; ",
        "<a href=\"https://twitter.com/", screen_name, "\">", screen_name, "</a>", "&nbsp;|&nbsp;",
        "<a href=\"https://twitter.com/",
        screen_name, "/status/", id, "\"> ", created, "</a> &nbsp;|&nbsp;",
        n_retweets, " retweets, ",  n_fav, " favorites. </blockquote>",
        "\n \n",
        sep = "")
}

for (i in seq_len(nrow(top_fav))) {
    render_tweet(top_fav, i)
}


```


## The 5 most retweeted tweets

```{r top-rt, echo=FALSE, results='asis'}
top_rt <- tw %>%
    filter(!is_retweet) %>%
    top_n(5, retweet_count)  %>%
    arrange(desc(retweet_count))

for (i in seq_len(nrow(top_fav))) {
    render_tweet(top_rt, i)
}

```

## Top tweeters

All generated tweets (including retweets)

```{r top-users-all, echo=FALSE, fig.height=10, fig.width=8}
top_users <- tw %>%
    group_by(screen_name) %>%
    summarize(total_tweets = n(),
              retweet = sum(is_retweet),
              original = sum(!is_retweet)) %>%
    top_n(30, total_tweets) %>%
    gather(type, n_tweets, -screen_name, -total_tweets)

top_users$screen_name <- reorder(top_users$screen_name,
                                 top_users$total_tweets,
                                 function(x) sum(x))

ggplot(top_users) + geom_bar(aes(x = screen_name, y = n_tweets, fill = type),
                             stat = "identity") +
  ylab("Number of tweets") + xlab("User") +
  coord_flip() +
  scale_fill_manual(values = wes_palette("Zissou")[c(1, 3)]) +
  theme(axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))
```

Only for original tweets (retweets excluded)

```{r, top-users-orig, echo=FALSE, fig.height=10}
top_orig_users <- tw %>% group_by(screen_name) %>%
    summarize(total_tweets = n(),
              Retweet = sum(is_retweet),
              Original = sum(!is_retweet)) %>%
    top_n(30, Original)

top_orig_users$screen_name <- reorder(top_orig_users$screen_name,
                                     top_orig_users$Original,
                                     function(x) sum(x))

ggplot(top_orig_users) + geom_bar(aes(x = screen_name, y = Original), stat = "identity",
                                  fill = wes_palette("Zissou", 1)) +
  ylab("Number of tweets") + xlab("User") +
  coord_flip() +
  theme(axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))

```


## Most favorited/retweeted users

The figures below only include users who tweeted 5+ times, and don't include
retweets.

### Number of favorites received by users

```{r, fig.height=10, echo=FALSE}
impact <- tw %>%
    filter(!is_retweet) %>%
    group_by(screen_name) %>%
    summarize(n_tweets = n(),
              n_fav = sum(favorite_count),
              n_rt =  sum(retweet_count),
              mean_fav = mean(favorite_count),
              mean_rt = mean(retweet_count)) %>%
    filter(n_tweets >=  5)

### Most favorited
most_fav <- impact %>%
    top_n(30, n_fav)

most_fav$screen_name <- reorder(most_fav$screen_name,
                               most_fav$n_fav,
                               sort)

ggplot(most_fav) +
    geom_bar(aes(x = screen_name, y = n_fav),
             stat = "identity", fill = wes_palette("Zissou")[2]) +
  coord_flip() + xlab("User") + ylab("Total number of favorites") +
  theme(axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))
```

### Number of retweets received by users

```{r, fig.height=10, echo=FALSE}
## Most retweeted

most_rt <- impact %>%
    top_n(30, n_rt)

most_rt$screen_name <- reorder(most_rt$screen_name,
                              most_rt$n_rt,
                              sort)

ggplot(most_rt) +
    geom_bar(aes(x = screen_name, y = n_rt),
             stat = "identity", fill =  wes_palette("Zissou")[5]) +
  coord_flip() + xlab("User") + ylab("Total number of retweets") +
  theme(axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))
```

### Mean numbers of favorites received

```{r, fig.height=10, echo=FALSE}

### Mean favorites

hi_mean_fav <- impact %>%
    top_n(30, mean_fav)

hi_mean_fav$screen_name <- reorder(hi_mean_fav$screen_name,
                                  hi_mean_fav$mean_fav,
                                  sort)

ggplot(hi_mean_fav) +
    geom_bar(aes(x = screen_name, y = mean_fav),
             stat = "identity", fill = wes_palette("Zissou")[2]) +
  coord_flip() + xlab("User") + ylab("Number of favorites / tweets") +
  theme(axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))

```

### Mean numbers of retweets received

```{r, fig.height=10, echo=FALSE}

### Mean retweets

hi_mean_rt <- impact %>%
    top_n(30, mean_rt)

hi_mean_rt$screen_name <- reorder(hi_mean_rt$screen_name,
                                 hi_mean_rt$mean_rt,
                                 sort)

ggplot(hi_mean_rt) + geom_bar(aes(x = screen_name, y = mean_rt),
                           stat = "identity", fill = wes_palette("Zissou")[5]) +
  coord_flip() + xlab("User") + ylab("Number of retweets / tweets") +
  theme(axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))


```

## Word cloud

The top 100 words among the original tweets.

```{r word-cloud, echo=FALSE, fig.height=8, fig.width=8, cache=TRUE}
library(wordcloud)

pal <- wes_palette("Darjeeling", 8, type = "continuous")

tw_text_cleanup <- function(x) {
    x %>%
        gsub("(@|\\#)\\w+", "", .) %>%   # remove mentions/hashtags
        gsub("https?\\:\\/\\/\\w+\\.\\w+(\\/\\w+)*", "", .) %>% #remove urls
        gsub("\\bthe\\b", "", .) %>% # remove the
        gsub("amp", "", .) %>%  ## remove &
        gsub("\\bspp\\b", "species", .) %>% ## replace spp by species
        gsub('\\p{So}|\\p{Cn}', '', ., perl = TRUE)
}

tw %>%
    filter(!is_retweet) %>%
    .$text %>% paste(collapse = "") %>%
    gsub("(@|\\#)\\w+", "", .) %>%   # remove mentions/hashtags
    gsub("https?\\:\\/\\/\\w+\\.\\w+(\\/\\w+)*", "", .) %>% #remove urls
    gsub("\\bthe\\b", "", .) %>% # remove the
    gsub("amp", "", .) %>%  ## remove &
    gsub("\\bspp\\b", "species", .) %>% ## replace spp by species
    gsub('\\p{So}|\\p{Cn}', '', ., perl = TRUE) %>%
    wordcloud(max.words = 100, colors = pal, random.order = FALSE, scale = c(3, .7))

```

## Most used emojis


```{r emoji-prep, cache=TRUE, echo=FALSE}
## Save this page locally: https://unicodey.com/emoji-data/table.htm

emodict <- read_html("Emoji Catalog.htm") %>%
    html_table() %>%
    .[[1]]
names(emodict) <- make.unique(names(emodict))

emodict <- emodict %>%
    select_if(is.character) %>%
    rename(glyph = Name.6,
           long_name = Name.7)
```

```{r emoji, echo=FALSE, eval=FALSE}
## inspired by: http://livefreeordichotomize.com/2017/07/17/ropensci-slack-emojis/
emojis <- tw$text %>%
    str_extract_all("[\\uD83C-\\uDBFF\\uDC00-\\uDFFF]+") %>%
    unlist() %>%
    str_split("") %>% unlist() %>%
    table() %>% sort(decreasing = TRUE) %>% as_tibble() %>%
    set_names(c("glyph", "freq") ) %>%
    filter( ! str_detect(glyph, "^[-[:space:]]" ) ) %>%
    left_join(emodict, by = "glyph") %>%
    filter(!is.na(long_name)) %>%
    top_n(15, freq) %>%
    mutate(emoji_png = file.path("Emoji Catalog_files", Image))

render_row_emoji <- function(emoji_png, freq) {
    emos <- rep(emoji_png, freq)
    ## we add a transparent square of the same size of the emoji
    ## (so we don't need to scale), to have room to display the number
    ## of times it is represented
    emos <- c(emos, "transparent-64x64.png")
    loc_str <- paste0("+", 64*freq, "+0")
    image_read(emos) %>%
        image_scale("x64") %>%
        image_append() %>%
        image_background("white", flatten = FALSE) %>%
        image_annotate(as.character(freq), gravity = "west",
                       location = loc_str, size = 45, color = "black")
}

render_plot <- function(bars, path) {
    do.call("c", bars) %>%
        image_append(stack = TRUE) %>%
        image_background("white", flatten = FALSE)
}

emojis %>%
    dplyr::select(emoji_png, freq) %>%
    purrr::pmap(render_row_emoji) %>%
    render_plot

 ```


## Most commonly associated words


```{r word-pairs, echo=FALSE, fig.width=10}
## From: http://tidytextmining.com/nasa.html#word-co-ocurrences-and-correlations
evo_stop_words <- data_frame(word = c("evol2017", "rt", "https", "t.co",
                    "amp"))

tw_word <- tw %>%
    distinct(status_id, .keep_all = TRUE) %>%
    filter(!is_retweet) %>%
    mutate(text = tw_text_cleanup(text)) %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words, by = "word") %>%
    anti_join(evo_stop_words, by = "word") %>%
    filter(!grepl("^[0-9]+$", word))

#tw_word %>%
#    count(word, sort = TRUE)

tw_word_pairs <- tw_word %>%
    pairwise_count(word, status_id, sort = TRUE, upper = FALSE)


library(ggplot2)
library(igraph)
library(ggraph)

set.seed(1234)

tw_word_pairs %>%
  filter(n >= 10) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()

```

## Sentiment analysis


Very little negativity in the #Evol2017 tweets. Most positive before lunch, and in the evening.


```{r sentiment, echo=FALSE}
## from: http://tidytextmining.com/sentiment.html#sentiment-analysis-with-inner-join
library(lubridate)

tw_words_all  <- tw %>%
    distinct(status_id, .keep_all = TRUE) %>%
    filter(!is_retweet, created_at > as.Date("2017-06-24")) %>%
    mutate(minutes = as.numeric(difftime(created_at, min(.$created_at),
                                         units = "mins")),
           day = as.integer(difftime(created_at, min(.$created_at),
                                     units = "days"))) %>%
    mutate(text = tw_text_cleanup(text))

tw_words <- tw_words_all %>%
    unnest_tokens(word, text) %>%
    inner_join(get_sentiments("bing"), by="word") %>%
    count(day, index = minutes %/% 120, sentiment) %>%
    spread(sentiment, n, fill = 0) %>%
    mutate(sentiment = positive - negative)

tw_words %>%
    mutate(time=minutes(index)*120 + min(tw_words_all$created_at)) %>%
    ggplot(aes(time, sentiment, fill = as.factor(day))) +
    geom_col() +
	theme(legend.position = "none")

```